---
title: "Results"
---

For MI, bias and empirical standard deviations are identical for the MI-R and MI-a variants, because both approaches are based on the same pooled point estimates and differ only in the degrees-of-freedom calculation used for inference. Therefore, MI-R and MI-a are reported separately only for coverage and confidence interval width.

For the level-1 effect $\gamma_{10}$, bias was consistently negligible relative to the corresponding MCSEs. Coverage, empirical standard deviations, and confidence/credible interval widths were comparable across methods and closely aligned with the corresponding CD results. Results are therefore reported here only for the level-2 effect $\gamma_{01}$. Full results for all parameters of interest and performance measures are provided in @sec-appB.

## Bias of point estimation
The findings for $\gamma_{01}$ are depicted in [@fig-bias] for all conditions with MAR. Results under MCAR followed very similar patterns and are therefore not shown separately. LD resulted in substantial bias, especially in conditions with low ICC. For a true null effect, estimates were positively biased, with a maximum of $0.042$. For a positive level-2 effect, estimates were negatively biased, with a maximum of $-0.050$. The magnitude of bias was similar across sample sizes and did not differ markedly between MAR and MCAR conditions. MI resulted in larger bias than LD in several low-ICC conditions with a substantial true effect, where bias ranged from $-0.044$ to $-0.078$, corresponding to approximately 10-20% of the true effect^[However, in a sensitivity analysis, the use of alternative weakly informative priors in these conditions consistently reduced bias by approximately 30–60% (see [@sec-appC] for details).]. In all other conditions, bias estimates for MI were small relative to their MCSEs (all $|\text{bias}| \leq 0.02$). In contrast, the Bayesian approach showed only small bias across all simulation conditions except the most challenging conditions ($N_2 = 15$, $ICC = .1$, $\gamma_{01} = 0.4$), where bias was $-0.039$ (MAR) and $-0.036$ (MCAR). These values remained below 10% of the true effect. All other biases were small ($|\text{bias}| \leq 0.015$).

```{r, echo=FALSE, message=FALSE}
#| label: fig-bias
#| fig.cap: "Bias of the between-group effect $\\gamma_{01}$ across simulation conditions under missing at random (MAR). Error bars represent ±2 Monte Carlo standard errors (MCSE). ES = effect size; ICC = intraclass correlation coefficient used for both the residual ICC of $Y$ and the ICC of $X$; $N_2$ = number of groups."
#| fig.scap: "Bias of $\\gamma_{01}$ across simulation conditions under MAR."
#| fig-asp: 0.9
#| out-width: 100%
library(here)
source(here("code", "bias-plot_script.R"))
print(bias_plot)

```

## Coverage rates of confidence and credible intervals
The results for coverage of the confidence and credible intervals for $\gamma_{01}$ are shown for $N_2 = 15$ in @fig-cov, as larger sample sizes exhibited similar but attenuated patterns. Overall, coverage rates were close to the nominal level (95%) for $N_2 = 30$ and $N_2 = 60$ across all methods. LD yielded coverage rates close to the nominal level in all conditions. For MI, coverage in the MI-R variant was close to the nominal level in high-ICC conditions, with a tendency toward overcoverage in low-ICC conditions. For $ICC = .1$, coverage ranged from 0.952 ($N_2 = 30$, $\gamma_{01} = 0.4$, MAR) to 0.971 ($N_2 = 60$, $\gamma_{01} = 0$, MCAR). The approach using small-sample adjusted degrees of freedom resulted in increased overcoverage compared to the standard degrees of freedom, particularly for $N_2 = 15$. Overcoverage was again more pronounced in low-ICC conditions, ranging from 0.960 ($N_2 = 60$, $\gamma_{01} = 0.4$, MCAR) to 0.986 ($N_2 = 15$, $\gamma_{01} = 0$, MCAR) for $ICC = .1$. The Bayesian approach exhibited overcoverage for $N_2 = 15$, ranging from 0.963 ($\gamma_{01} = 0$, MCAR, $ICC = .1$) to 0.985 ($\gamma_{01} = 0.4$, MCAR, $ICC = .1$). This method yielded the highest (most conservative) coverage rates at the smallest level-2 sample size, except in the condition with MCAR, $ICC = .1$, and $\gamma_{01} = 0$. With increasing level-2 sample size, this pattern attenuated. For $N_2 = 30$, coverage estimates were largely within the bounds of Monte Carlo error, and for $N_2 = 60$, they fell entirely within these bounds across all conditions.
```{r, echo=FALSE, message=FALSE}
#| label: fig-cov
#| fig.cap: "Deviation from nominal (95%) coverage of confidence/credible intervals across methods and simulation conditions for $N_2 = 15$. Error bars represent ±2 Monte Carlo standard errors (MCSE). ES = effect size; MAR = missing at random; MCAR = missing completely at random; ICC = intraclass correlation coefficient used for both the residual ICC of $Y$ and the ICC of $X$; MI-Rubin = multiple imputation using Rubin's degrees of freedom; MI-adjusted = multiple imputation using adjusted degrees of freedom."
#| fig.scap: "Coverage performance for $N_2=15$"
#| fig-asp: 0.45
#| out-width: 100%
library(here)
source(here("code", "cov-plot_script.R"))
print(cov_plot)

```
## Standard deviation of point estimates
Standard deviations of point estimates across conditions and methods are illustrated in @fig-sd for MAR, as differences between missingness mechanisms were small. LD produced standard deviations very close to those obtained under CD, ranging from 0.124 ($N_2 = 60$, MCAR, $\gamma_{01} = 0.4$) to 0.300 ($N_2 = 15$, MCAR, $\gamma_{01} = 0$). For MI, standard deviations were comparable to CD across conditions, with a tendency toward smaller values in some low-ICC conditions. For example, for $N_2 = 15$, $\gamma_{01} = 0$, and MAR missingness, MI yielded a standard deviation of 0.247, compared to 0.283 under CD. The Bayesian approach yielded standard deviations that were generally slightly larger than those from CD, typically by approximately 0.006 to 0.020. Standard deviations were generally smaller under high ICC conditions than under low ICC conditions in the Bayesian framework, except in the conditions with $\gamma_{01} = 0.4$ and $N_2 = 15$. In contrast, MI consistently yielded slightly larger standard deviations under high-ICC conditions. Although these differences were small, they were larger than would be expected from Monte Carlo error alone.
```{r echo=FALSE, message=FALSE}
#| label: fig-sd
#| fig.cap: "Empirical standard deviation (SD) of point estimates for $\\gamma_{01}$ for conditions with missingness at random (MAR). Error bars represent ±2 Monte Carlo standard errors (MCSE). $N_2$ = number of groups; ICC = intraclass correlation coefficient used for both the residual ICC of $Y$ and the ICC of $X$."
#| fig.scap: "Empirical standard deviations for $\\gamma_{01}$ under MAR"
#| fig-asp: 0.45
#| out-width: 100%

library(here)

# read in script
source(file = here("code", "sd-plot_script.R"))

# make plot
print(sd_plot)

```
## Width of confidence and credible intervals
Results for the width of confidence and credible intervals are illustrated in @fig-ciw for the three conditions with $\gamma_{01} = 0.4$, under MAR and with $ICC = .1$, as similar patterns were observed across the other conditions. Overall, the Bayesian approach yielded the widest credible intervals, followed by MI with adjusted degrees of freedom (MI-a). For $N_2 = 15$, the MI-R variant produced interval widths that were slightly smaller than those obtained under CD (e.g., 1.115 vs. 1.170 for MCAR, $ICC = .1$, $\gamma_{01} = 0$). For $N_2 = 30$ and $N_2 = 60$, MI-R interval widths were slightly larger than those from CD, while still remaining smaller than those from MI-a and the Bayesian approach. Confidence intervals from LD were similar to those obtained with CD across conditions. 

At the smallest level-2 sample size, $N_2 = 15$, differences between methods were most pronounced. For example, when $\gamma_{01} = 0$ and $ICC = .1$ under MCAR, interval width for $\gamma_{01}$ was 1.115 under MI-R, 1.284 with MI-a and 1.456 under the Bayesian approach. With increasing level-2 sample size, differences between methods became less pronounced, although interval widths for the Bayesian approach remained slightly larger. For instance, when $\gamma_{01} = 0$, $ICC = .1$, and MCAR at $N_2 = 60$, interval width was 0.517 for CD, 0.520 for LD, 0.545 for MI-R, 0.559 for MI-a, and 0.582 for the Bayesian approach. Within the fully Bayesian approach, interval widths were generally slightly smaller under high-ICC conditions than under low-ICC conditions. In contrast, the other methods did not show a consistent ICC-related pattern. 

```{r echo=FALSE, message=FALSE}
#| label: fig-ciw
#| fig.cap: "Width of confidence/credible intervals for $\\gamma_{01} = 0.4$ under missing at random (MAR) and $ICC = .1$, where ICC denotes the intraclass correlation coefficient used for both the residual ICC of $Y$ and the ICC of $X$. Error bars represent ±2 Monte Carlo standard errors (MCSE). $N_2$ = number of groups; MI-Rubin = multiple imputation with Rubin's degrees of freedom; MI-adjusted = multiple imputation with small-sample-adjusted degrees of freedom."
#| fig.scap: "Width of confidence/credible intervals for $\\gamma_{01}=0.4$"
#| fig-asp: 0.45
#| out-width: 100%


# read in script
source(file = here("code", "ciw-plot_script.R"))

# make plot
print(ciw_plot)

```

## Summary of results
The methods showed different performance profiles for the level-2 effect. LD resulted in increased bias, while other performance measures were generally similar to CD results. MI produced substantial downward bias in the estimation of the level-2 effect under conditions of low ICC and MAR missingness. At the same time, the standard variant (MI-R) yielded coverage rates close to the nominal level across conditions. Applying a small-sample correction to the degrees of freedom led to increased coverage beyond the nominal level and wider confidence intervals. The fully Bayesian approach showed small to negligible bias across conditions, but resulted in the widest intervals among all methods and a tendency toward overcoverage in the smallest sample size.