---
title: "Results"
---
The complete results for the parameters of interest are provided in tables in [@sec-appB].

## Bias of point estimation
In line with expectations, no substantial bias was observed for the individual-level effect $\gamma_{10}$. 
The findings for $\gamma_{01}$ are depicted in [@fig-bias].
For $\gamma_{01}$, listwise deletion produced substantial bias, especially in low-ICC conditions, with positive bias for the null effect and negative bias for the positive between-group effect. With increasing sample size and under MAR condition, this bias was more pronounced.  
Multiple imputation showed even larger bias than listwise deletion in conditions with low ICC and positive effect^[However, using alternative weakly informative priors in these conditions consistently reduced bias by roughly 30–60%.]In contrast, the Bayesian approach only led to noticeable bias in the most challenging conditions (smallest sample size, low ICC and positive $\gamma_{01}$-effect}.

```{r, results='asis', echo=FALSE, message=FALSE}
#| label: fig-bias
#| caption: "Figure caption"
#| fig-asp: 1.3
#| out-width: 100%
library(here)
library(patchwork)
source(here("code", "bias-plot_script.R"))
wrap_plots(A = plotbias15, B = plotbias30, C = plotbias60, design = "AA\nBB\nCC")
```

## Coverage of confidence/credible intervals
The coverage of the confidence and credible intervals for $\gamma_{01}$ is shown for $N_2 = 15$ in [@fig-cov], as coverage for larger sample sizes was largely within the acceptable range of 0.925–0.975.

Listwise deletion yielded coverage rates close to the nominal 95% level across all conditions. For multiple imputation, the small-sample adjusted degrees of freedom resulted in increased overcoverage compared to the standard degrees of freedom, particularly when $N_2 = 15$, with a similar but weaker tendency at larger sample sizes. The Bayesian approach showed even stronger overcoverage in the smallest sample.

Overall, MI with standard degrees of freedom (MI-R) and listwise deletion provided coverage closest to the nominal level, whereas noticeable deviations occurred mainly in the smallest sample for the other methods.

HIER NOCH ANDERE PLOTS ODER REICHT EINER?
ODER MAL NUR TABELLE?


```{r, results='asis', echo=FALSE, message=FALSE}
#| label: fig-cov
#| caption: "Coverage"
#| fig-asp: 0.5
#| out-width: 80%
# packages
library(here)
library(dplyr) 
library(tidyr)
library(knitr)
library(ggplot2)

# read in results and functions
results <- read.table(file = here("results", "summarized_simulation-results.csv"))
source(file = here("code", "functions", "condition-table_function.R"))
source(file = here("code", "functions", "coverage-plot_function.R"))
info15l <- make_condition_table(results, N2_filter = 15)

plot_cov(results, info15l, N2_filter = 15,
                           methods = c("CD", "LD", "MI-R", "MI-a", "bayes"))

```

## Standard deviation of point estimates
