---
title: "Results"
---
The complete results for the parameters of interest are provided in tables in [@sec-appB].

## Bias of point estimation
In line with expectations, no substantial bias was observed for the individual-level effect $\gamma_{10}$.   
The findings for $\gamma_{01}$ are depicted in [@fig-bias].
For $\gamma_{01}$, listwise deletion produced substantial bias, especially in low-ICC conditions, with positive bias for the null effect and negative bias for the positive between-group effect. With increasing sample size and under MAR condition, this bias was more pronounced.  
Multiple imputation showed even larger bias than listwise deletion in conditions with low ICC and positive effect^[However, in a sensitivity analysis, usage of alternative weakly informative priors in these conditions consistently reduced bias by roughly 30–60% (see [@sec-appC] for details).]. In contrast, the Bayesian approach only led to noticeable bias in the most challenging conditions (smallest sample size, low ICC and positive $\gamma_{01}$-effect).

```{r, echo=FALSE, message=FALSE}
#| label: fig-bias
#| fig.cap: "Hier noch Caption"
#| fig-asp: 1
#| out-width: 90%
library(here)
source(here("code", "bias-plot_script.R"))
print(bias_plot)

```

## Coverage of confidence/credible intervals
The coverage of the confidence and credible intervals for $\gamma_{01}$ is shown for $N_2 = 15$ in [@fig-cov], as coverage for larger sample sizes was largely within the acceptable range of 0.925–0.975.

Listwise deletion yielded coverage rates close to the nominal 95% level across all conditions. For multiple imputation, the small-sample adjusted degrees of freedom resulted in increased overcoverage compared to the standard degrees of freedom, particularly when $N_2 = 15$, with a similar but weaker tendency at larger sample sizes. The Bayesian approach showed even stronger overcoverage in the smallest sample, but not for $N_2 = 30$ and $N_2 = 60$.

Overall, MI with standard degrees of freedom (MI-R) and listwise deletion provided coverage closest to the nominal level, whereas noticeable deviations occurred mainly in the smallest Level-2 sample for the other methods.


```{r, echo=FALSE, message=FALSE}
#| label: fig-cov
#| fig.cap: "Coverage TEXT TEXT TEXT HIER HIN NOCH TEXT "
#| fig-asp: 0.45
#| out-width: 90%
library(here)
source(here("code", "cov-plot_script.R"))
print(cov_plot)

```

## Standard deviation of point estimates
No substantial differences between methods for the parameter $\gamma_{10}$ were observed, except for the complete-data condition, which consistently yielded the smallest standard deviations.  
Interestingly, for $\gamma_{10}$, the variability of point estimates across simulation repetitions was smallest for multiple imputation in low-ICC conditions and similar to complete data analysis for high-ICC, whereas the Bayesian approach produced the largest standard deviations across all conditions (see @fig-sd). A systematic tendency was visible: Multiple imputation standard deviations decreased with a low ICC, whereas in the Bayesian approach, they decreased with a high ICC for $N_2 = 30$ and $N_2 = 60$.
Listwise deletion shows very similar results to complete data analysis regarding standard deviation.  
Differences between methods are overall quite small, with MI SD being smaller than Bayes SD by a maximum of ~14.5%.  

*Hier eher Tabelle statt Grafik?*


```{r echo=FALSE, message=FALSE}
#| label: fig-sd
#| fig.cap: "blablabalbslsd"
#| fig-asp: 0.5
#| out-width: 90%

# packages
library(here)
library(dplyr) # for data grouping
library(tidyr)
library(knitr)
library(ggplot2)

# read in script
source(file = here("code", "sd-plot_script.R"))

# make plot
print(sd_plot)

```

## Width of confidence / credible intervals
No noteworthy differences were observed for $\gamma_{10}$.  
For $\gamma_{01}$, interval widths were relatively stable within each sample size, but there were differences between methods. Bayesian credible intervals were consistently the widest, followed by the MI-a approach. Confidence intervals from the MI with Rubin´s degrees of freedom were even narrower than CD/LD for $N_2 = 15$, although these differences were small in magnitude.  
These results are shown in an exemplary manner in @fig-ciw.


```{r echo=FALSE, message=FALSE}
#| label: fig-ciw
#| fig.cap: "blablabalbslsd"
#| fig-asp: 0.5
#| out-width: 50%


# read in script
source(file = here("code", "ciw-plot_script.R"))

# make plot
print(ciw_plot)

```
## Summary of results
Across all performance criteria, only small differences between methods were observed for the individual-level effect $\gamma_{10}$.  
Regarding $\gamma_{01}$, listwise deletion showed increased bias but acceptable coverage. Multiple imputation led to higher bias than the Bayesian approach in several challenging conditions. MI-a produced higher overcoverage and wider confidence intervals compared to the MI-R variant; the Bayesian method generally resulted in the highest overcoverage and the widest credible intervals.
